---
title: "Group project 2"
author: Lorraine Li, Oliver Zhang, Chentuo Hu, Zifan Liu, Xue Liu, Yuchen Li, Jeremiah Lee
date: "9/9/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

question(a) Produce a scatterplot matrix which includes all of the variables in the data set.
```{r}
library(ISLR)
Auto = na.omit(Auto)
attach(Auto)
pairs(Auto)
# using pairs function, we plot the scatterplot matrix.
```


question(b) Compute the matrix of correlations between the variables using the function cor(). You will need to exclude the name variable, which is qualitative.
```{r}
auto_df=subset(Auto, select=-c(name))
cor(auto_df)
# We use -c(name) to exclude the name variable then use cor() function to compute the correlations between all the variable in this subset auto_df
```
question (c) Use the lm() function to perform a multiple linear regression with mpg as the response and all other variables except name as the predictors. Use the summary() function to print the results.
i. Is there a relationship between the predictors and the response?
ii. Which predictors appear to have a statistically significant relationship to the response?
iii. What does the coefficient for the year variable suggest?
```{r}
auto_df=subset(Auto, select=-c(name))
mpg_regression = lm(mpg ~.,data = auto_df)
summary(mpg_regression)
#i. According to the number of asterisks that summary(mpg_regression) shows, we can observe that there are some relationships between MPG and displacement, weight, year and origin. The rest of predictors barely show statistically significant, the Adjusted R-squared equals to 0.8182 which means most of the change in predictors can cause change in target value
#ii. Displacement, weight,year and origin are the predictors that have significant relationship to the target value mpg.
#iii.The estimate figure of coefficient is pretty high 0.75,and the p-value of this regression is really small, which means this regression is successful so we think the relationship is obvious. when the year increased by 1, mpg increases about 0.75.
```
question (d) Use the plot() function to produce diagnostic plots of the linear regression fit. Comment on any problems you see with the fit. Do the residual plots suggest any unusually large outliers? Does the leverage plot identify any observations with unusually high leverage?
```{r}
par(mfrow = c(2, 2))
plot(mpg_regression)
# we use par(mfrow = c(2,2)) to place 4 plot graphs in one picture. 
# From the first plot graph we can see that there is no linear relationship between the target values and the predictors.
# The second plot graph shows that distribution of dataset is close to the normal distribution
# From the last graph we can tell that the point 14 is likely to be a leverage point.
```

question (e) Use the * and : symbols to fit linear regression models with interaction effects. Do any interactions appear to be statistically significant?

```{r}
x = lm(mpg~. -name, data = Auto)
summary(x)
# from this regression model, we select parts of predictors that show statistical significance in predicting mpg and add some factors that may have influence on mpg based on our common sense . cylinders,displacement,origion,weight,year
x1 = lm(mpg~cylinders*displacement + weight + horsepower + weight*horsepower, data = auto_df)
summary(x1)
x2 = lm(mpg ~. - name +displacement:cylinders+displacement:weight+acceleration:horsepower, data=auto_df)
summary(x2)
#it seems that cylinders is not a crutial factor when predicting mpg, including its interaction with other variables.
x_all_the_interaction = lm(formula = mpg ~ . - name - cylinders  + year:origin + displacement:weight + displacement:weight + acceleration:horsepower + acceleration:weight, data = Auto)
summary(x_all_the_interaction)
```
## summary : As we can see from these models above, when we add interaction of different variables in the regression, the significance of all the interactions and variables themselve increases, and model x_all_the_interaction seems to be the most suitable model in predicting mpg. The R squared value reaches 86.6%, which means nearly 87% of the changes in the mpg are caused by the predictors(variables and interactions) in thismodel.

question(f) Try a few different transformations of the variables, such as log(X), √X, X2. Comment on your findings.
```{r}
test_regression = lm(mpg ~.-name + sqrt(displacement) + sqrt(weight), data = Auto)
summary(test_regression)
test_regression1 = lm(mpg ~.-name + sqrt(displacement) + log(weight), data = Auto)
summary(test_regression1)
test_regression2 = lm(mpg ~.-name + sqrt(displacement) + sqrt(weight) + log(year) + sqrt(year), data = Auto)
summary(test_regression2)
```
## summary : When adding the transformations of the variables, the outcome of regression model would change. However, no matter the changes in predictors, variable year seems to be a competitive one in influencing mpg.